\documentclass[12pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[margin=2cm]{geometry}
\title{Amr's Cover Letter}
\author{Amr Wahdan}
\date{}

\newcommand{\fancy}[1]{\Large\textbf{\textit{#1}}}

\begin{document}
\pagenumbering{gobble}

%%% Header info %%%

\begin{tabular}{@{}l@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
    \begin{minipage}{0.6\textwidth}
        \resizebox{.9\linewidth}{!}{\itshape AMR} \\
        \resizebox{.9\linewidth}{!}{\itshape WAHDAN}
    \end{minipage} &
    \begin{minipage}{0.3\textwidth}
		\vspace{2em}
        Alexandria, Egypt \\
		\vspace{.5pt} \\
        aaamwahdan@gmail.com \\ 
		\vspace{.5pt} \\
        (+20) 106 235 6288 \\
		\vspace{.5pt} \\
        \textbf{November 7th, 2024}
		\vspace{1em} \\
    \end{minipage}
\end{tabular}

\vspace{1em}

\begin{center}
	\fancy{Söderhub -- Business Analyst application}
\end{center}

\vspace{2em}

Dear Söderhub Hiring Team,

\vspace{1em}

I am thrilled to apply for the Business Analyst Intern position at Söderhub, as advertised. This role aligns perfectly with my deep passion for business processes and market analysis, and I am genuinely excited about the prospect of contributing to a company renowned for bridging Nordic and MENA opportunities. With my background in computer science and statistics and hands-on experience in client acquisition and business development, I am confident I will bring both analytical acumen and a strong drive to excel to the Söderhub team. \par

\vspace{1em}
In my recent position as a Business Development Manager at Nedialo, I developed a keen ability to interpret data insights to drive new client acquisition and optimize business operations. My role required a meticulous approach to analyzing business needs, creating structured client onboarding processes, and fostering productive client relationships. Additionally, my role as a Cold Caller at Teletarget enhanced my adaptability and helped me gain valuable skills in engaging stakeholders and interpreting market feedback—essential for this internship’s focus on market research, operations, and customer success. \par

\vspace{1em}
I am well-versed in tools such as Google Suite and LaTeX, which has equipped me to contribute effectively to project documentation and digital marketing tasks. My academic and project experience in R and Python allows me to analyze data and derive insights, which I look forward to applying to support the Söderhub team’s market and operations initiatives. \par

\vspace{1em}
I am enthusiastic about the opportunity to work with Söderhub's ambitious team in Egypt, and I am particularly inspired by Söderhub's mission to create a “southern hub” for Nordic companies in the MENA region. I am confident that my analytical skills, attention to detail, and strong commitment to organizational success will enable me to make a positive impact. \par

\vspace{1em}
Thank you for considering my application. I look forward to the opportunity to discuss how my background and skills align with Söderhub's goals.


\vspace{1.5em}

\textit{-----Sincerely,}

\vspace{1em}

\fancy{Amr Wahdan}

\end{document}
