\documentclass[12pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[margin=2cm]{geometry}
\title{Amr's Cover Letter}
\author{Amr Wahdan}
\date{}

\newcommand{\fancy}[1]{\Large\textbf{\textit{#1}}}

\begin{document}
\pagenumbering{gobble}

%%% Header info %%%

\begin{tabular}{@{}l@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
    \begin{minipage}{0.6\textwidth}
        \resizebox{.9\linewidth}{!}{\itshape AMR} \\
        \resizebox{.9\linewidth}{!}{\itshape WAHDAN}
    \end{minipage} &
    \begin{minipage}{0.3\textwidth}
		\vspace{2em}
        Alexandria, Egypt \\
		\vspace{.5pt} \\
        aaamwahdan@gmail.com \\ 
		\vspace{.5pt} \\
        (+20) 106 235 6288 \\
		\vspace{.5pt} \\
        \textbf{November 21th, 2024}
		\vspace{1em} \\
    \end{minipage}
\end{tabular}

\vspace{1em}

\begin{center}
	\fancy{Fantastic Services -- Corporate Account Agent}
\end{center}

\vspace{2em}

Dear Fantastic Services Team,

\vspace{1em}

I am thrilled to apply for the Corporate Account Agent role at Fantastic Services. This role aligns perfectly with my deep passion for business development and market analysis, and I am genuinely excited about the prospect of contributing to a company like Fantastic Services. With my background in computer science and statistics and hands-on experience in client acquisition and business development, I am confident I will bring both analytical acumen and a strong drive to excel to the Fantastic Services team. \par

\vspace{1em}
In my recent position as a Business Development Manager at Nedialo, I developed a keen ability to interpret data insights to drive new client acquisitions and optimize business operations. My role required a meticulous approach to analyzing business needs, creating structured client onboarding processes, and fostering productive client relationships. There, I helped Nedialo start a cold emailing campaign to drive up sales with the help of another company I introduced them to via my network -- iSkala. I then went on to manage the communication between those two companies, track the results, and developed SOP's to handle the resulting onboardings. I also helped analyze company data to eventually find out that we get more clients from roofing businesses instead of real estate businesses and thus suggested switching a bigger part of our operations to roofing clients instead of real estate ones.

\vspace{1em}
I am well-versed in tools such as Google Suite and LaTeX, which has equipped me to contribute effectively to project documentation and digital marketing tasks. My academic and project experience in R and Python allows me to analyze data and derive insights, which I look forward to applying to support the Fantastic Services team’s market and operations initiatives. \par

\vspace{1em}
Thank you for considering my application. I look forward to the opportunity to discuss how my background and skills align with Fantastic Services's goals.


\vspace{1.5em}

\textit{-----Sincerely,}

\vspace{1em}

\fancy{Amr Wahdan}

\end{document}
